% !TEX root =  paper.tex
\section{Preliminary Study}
\label{sec:tapulator}

To evaluate the potential of the gestures, we compare the Espresso method to a standard accessible numeric keyboard entry method, VoiceOver, using 
  \begin{enumerate*}[(1) ]
    \item a theoretical analysis of the methods and 
    \item an empirical comparison with five users. 
  \end{enumerate*}
We choose the Espresso method over the Cappuccinno method because it is more intuitive to learn.

\subsection{Theoretical Analysis}
In the standard method, there are two steps involved in entering a digit. First, the user has to explore the screen to locate the button where the digit resides. The seek time is hard to quantify, but it requires listening to the buttons touched until the correct one is found. Once the button is located, the user performs a selection gesture. One selection gesture is a split tap, holding a finger down on the target button and using another finger to tap the screen. Another selection gesture is one-finger double tap anywhere on the screen. At a first attempt, this method appears to be more difficult than the 2.1 taps per digit.

\subsection{Empirical Evaluation}
Our empirical evaluation consists of a study with five sighted participants. In each of the study, the participants entered 10 six-digit numbers using the standard and the Espresso methods. Participants held the smartphone beneath the desk so that they were not able to see the screen. After a brief practice session, the participants achieved an average number entry rate of 1.99 seconds per digit ($SD = 1.25$) and 2.77 seconds per digit ($SD = 1.24$) using the Espresso method and the standard VoiceOver method, respectively. The error rates were far lower in the Espresso method than in the VoiceOver method. The participants averaged a Mean String Distance (MSD)\footnote{Defined as $\sum \mbox{distance from original string} \div \mbox{total digits} $} of only 1\% using Espresso method. Whereas, using the standard method, the participants achieved a MSD of 14.2\% on average. The Espresso method out-performed the standard method in both speed and accuracy. Unsurprisingly, all five participants perferred the Espresso method to the standard method \cite{Ruamviboonsuk:2012}.
\par
While the results are from a preliminary study, they show that the Espresso method has potential to out-perform the standard numeric entry method. We decided to conduct an extensive study not only on the Espresso method, but on both the Espresso and the Cappuccino methods.